Title Goes Here

### 2017-08-19 analysis/paper/paper.Rmd
can't use log scale with bar plot

 years_of_interest <- c(1957, 1990, 2009)
 ymax <- 15000
date_plot2 <- 
  dates %>% 
  filter(datacentre %in% top_data_sources) %>% 
  ggplot(aes(yyyy_date)) +
  geom_bar(aes(fill = datacentre)) +
  scale_y_log10(limits = c(1, ymax)) +
  scale_fill_viridis(discrete = TRUE) +
  theme_new() +
  xlim(c(1900,2017)) +
  xlab("Year data was collected") +
  ylab("Number of archaeology DOIs\nknown to DataCite") +
  geom_vline(xintercept = years_of_interest, colour = "red") +
  annotate("text", 
           x = years_of_interest + 4,
           y = ymax,
           label = years_of_interest)

>>>>

 years_of_interest <- c(1990, 2009)
 ymax <- 10000
date_plot2 <- 
  dates  %>% 
  filter(!is.na(yyyy_date)) %>% 
  ggplot(aes(yyyy_date,
             fill = datacentre_symbol
             )) +
  geom_bar() +
  guides(fill=FALSE) +
  scale_fill_viridis(discrete = TRUE) +
  theme_new() +
  xlim(c(1950,2017)) +
  xlab("Year data was collected") +
  ylab("Number of archaeology DOIs\nknown to DataCite") +
  geom_vline(xintercept = years_of_interest, colour = "red") +
  annotate("text", 
           x = years_of_interest + 2,
           y = ymax,
           label = years_of_interest)

# plotly::ggplotly(date_plot2) %>%
#   layout(showlegend = FALSE)
